A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 skeleton_and_pathtracing.tex
Corrections de l'intro par michel

A path tracing algorithm sends rays (of light) from the camera (the viewpoint of the scene), and let them bounce around the scene until they encounter a light source. When a ray hit a point of an object (like a wall), it gathers some information on the object's material. The ray is then reemitted in a random direction. Once a ray reaches a light source, the information it gathered through its journey in the scene is averaged in order to decide of the colour of the first impact point. This color is then allocated to one of the pixel of the image, and the process is repeated for each pixel of the output image. To avoid \quotes{unrealistic} results due to an unusual reemission direction of a ray, the algorithm actually sends, for each pixel of the image, many rays: the more rays, the longer the algorithm will take to produce an image, but the more realistic the result will look. A path tracing can be seen as a random walk process through the scene.

The bouncing direction of a ray depends on a function associated to the texture of the hit point: this probability distribution function gives, for a given incoming direction, the probability of reemitting the ray in another directions. The bouncing direction is randomly chosen among the possible values of this function. Choosing only one bouncing direction produces a noise in the resulting image (due, as previously said, to points where unusual directions were chosen): this noise is naturally reduced by shooting many rays for each image pixel (however, it will remain).

@@

Our proposition is to reduce both the time taken by a path tracing algorithms and the noise in the output images by guiding rays towards the scene's light sources, thus reducing the number of rays \quotes{lost} during the computation. To do this, we could perform some precomputation on the void space of the scene (the medium where the rays of light propagate) in order to have, later in the algorithm, a clue on towards which direction a ray should bounce in order to meet a light source. Such precomputation can take time and become more expensive than the original algorithm.

To keep the precomputation fast, we would perform it only on a subset of points of the voids of the scene. The precomputation we want to perform relies on shortest paths and visibility tests, we therefore want to have a reduced connected set of points (topology preservation). Moreover, in order to obtain correct results, this set of points should contain geometrical information from the original scene (for example, it should possess branches propagating in the elongated parts of the scene).

A filtered curvilinear skeleton of the voids of the scene would meet all the required properties for our subset of points: it is a thin subset of points of the scene, with the same topology and retaining the main geometrical information of the scene (if the filtering step is efficient). In the following, we first present a new curvilinear skeletonization algorithm (Sec.~\ref{sec::skeletonization}) in the cubical complex framework (Sec.~\ref{sec::binary_to_cubic}), producing filtered skeletons without needing any user input (Sec.~\ref{sec::aspect_no_param}). Then, we show how to use such skeletons to enhance the results of a path tracing algorithm (see Sec.~\ref{sec::appli_pathtrace}).

>>>>

A path tracing algorithm sends rays (of light) from the camera (the viewpoint of the scene), and let them bounce around the scene until they encounter a light source. When a ray hits a point of an object (like a wall), it gathers information on the object's material. The ray is then reemitted in a random direction. Once a ray reaches a light source, the information it gathered through its journey in the scene is averaged in order to decide of the color of the first impact point. This color is then allocated to one of the pixels of the image, and the process is repeated for each pixel of the output image. To avoid \quotes{unrealistic} results due to an unusual reemission direction of a ray, the algorithm actually sends, for each pixel of the image, many rays: the more rays, the longer the algorithm will take to produce an image, but the more realistic the result will look. A path tracing can be seen as a random walk process through the scene.

@@

Our proposition is to reduce both the time taken by a path tracing algorithms and the noise in the output images by guiding rays towards the scene's light sources, thus reducing the number of rays \quotes{lost} during the computation. To do this, we perform some precomputation on the void space of the scene (the medium where the rays of light propagate) in order to have, later in the algorithm, a clue on towards which direction a ray should bounce in order to meet a light source. Such precomputation can take time and become more expensive than the original algorithm.

To keep the precomputation fast, we perform it only on a subset of points of the voids of the scene. The precomputation we want to perform relies on paths and visibility tests, therefore want this set of points to be representative of both the topology and the geometry of the original scene. For example, it should possess branches propagating in the elongated parts of the scene. A filtered curvilinear skeleton of (the voids of) the scene meets all the required properties for our subset of points: it is a thin subset of points of the scene, with the same topology and retaining the main geometrical information of the scene. Note that in this application, the filtering of the skeleton (elimination of spurious branches) need to be both efficient and completely automatic, for one cannot ask a user to set parameters for each scene.

The purpose of this paper is twofold: we first introduce a new curvilinear skeletonization algorithm (Sec.~\ref{sec::skeletonization}) in the cubical complex framework (Sec.~\ref{sec::binary_to_cubic}), producing filtered skeletons without needing any user input (Sec.~\ref{sec::aspect_no_param}). 
Then, we expose a new method, based on such skeletons, to enhance the results and the performance of a path tracing algorithm (see Sec.~\ref{sec::appli_pathtrace}).
